---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# naijR
An R package on Nigeria and for Nigeria  

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/naijR)](https://cran.r-project.org/package=naijR)
[![Travis build status](https://travis-ci.org/BroVic/naijR.svg?branch=master)](https://travis-ci.org/BroVic/naijR)
[![Codecov test coverage](https://codecov.io/gh/BroVic/naijR/branch/master/graph/badge.svg)](https://codecov.io/gh/BroVic/naijR?branch=master)
<!-- badges: end -->

The goal of **naijR** is to make it easier for R users to work with data related to Nigeria.

## Usage
### Prerequisites
This is a package for use in the R ecosystem. To install R, visit <https://cran.r-project.org>.

### Installation
To download and install the current stable version of this package from [CRAN](https://cloud.r-project.org/web/packages/naijR/index.html):

```{r cran-install, eval=FALSE}
install.packages("naijR")
```

The development version can be obtained from [GitHub](https://github.com/BroVic/naijR) with:

``` {r install, eval = FALSE}
# If necessary, 'install.packages("remotes")' first
remotes::install_github("BroVic/naijR")
```

### Examples
#### States
To create a list of all the States of the Nigerian Federation, simply call `states()`

```{r}
library(naijR, quietly = TRUE)  # attach to R session
states()
```

States from a given geo-political zone can also be selected

```{r}
states(gpz = "ne")  # i.e. North-East
```

For other capabilities of this function, see `?states()`

#### Local Government Areas
This is a basic example that shows how to very quickly fetch the names of Local Government Areas within a given State:

```{r example}
lgas_ng("Imo")
```

To list all the LGAs in Nigeria, call the same function without any parameters:

```{r}
n <- length(lgas_ng())
sprintf("Nigeria has a total of %i Local Government Areas", n)
```

Want to create a function to check how many LGAs a particular State has?

```{r}
how_many_lgas <- function(state) {
  require(naijR)
  stopifnot(state %in% states())
  cat(sprintf("No. of LGAs in %s State:", state),
      length(lgas_ng(state)),
      fill = TRUE)
}

how_many_lgas("Sokoto")
how_many_lgas("Ekiti")
```

## Feedback
For bug reports or feature requests, submit an [issue](https://github.com/BroVic/naijR/issues/new).
