---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# naijR
An R package on Nigeria and for Nigeria  

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/DevSolutionsLtd/naijR.svg?branch=master)](https://travis-ci.org/DevSolutionsLtd/naijR)
[![Codecov test coverage](https://codecov.io/gh/DevSolutionsLtd/naijR/branch/master/graph/badge.svg)](https://codecov.io/gh/DevSolutionsLtd/naijR?branch=master)
<!-- badges: end -->

The goal of naijR is to make it easier for people R users to work with data related to R, as well as to draw the attention of Nigerian workers to R's superb facilities for data analysis and modelling.

## Installation

<!-- You can install the released version of naijR from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("naijR") -->
<!-- ``` -->

The development version of this package can be downloaded and installed from [GitHub](https://github.com/) with:

``` {r install, eval = FALSE}
# If necessary, first do 'install.packages("devtools")'
devtools::install_github("DevSolutionsLtd/naijR")
```
## Example

This is a basic example that shows how to very quickly fetch the names of Local Government Areas within a given State:

```{r example}
library(naijR, quietly = TRUE)
lgas_ng("Imo")
```
