---
title: "Approach to Correcting Misspelt Local Government Areas"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Approach to Correcting Misspelt Local Government Areas}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: inline
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  results = 'hide'
)
```

## Motivation
Nigeria has 774 Local Government Areas (LGAs). There a number of factors that can make working with them challenging:

1. Some LGAs share the same name with their respective States e.g. Bauchi LGA in Bauchi State, and this can lead to wrong application of the data.
2. Some LGAs bear the same name although they are in different States, e.g. Obi LGA in Benue and Nasarawa States.
3. LGA spelling discrepancies are rife in the literature, and believe it or not, even in official government documents. 

## A proposed solution
The function `fix_region` is designed to address spelling errors in the sub-national administrative regions of Nigeria, beginning with States and LGAs. 

### States
For the States this is straightforward; minor mistakes can be corrected automatically with this function and since there are only 36 of them, they can also be corrected via an inspection of the output from a call to `states()`.

### LGAs
Fixes to LGA spellings are designed to occur in 3 incremental phases. If the user cannot effect the corrections at a particular level s/he can proceed to the next stage. The phases are as follows:

1. Automatic
2. Interactive
3. Manual

#### 1. Automatic fixes
When the spelling error is slight and unambiguous, the function automatically effects the repair. However, when there is only a single misspelt LGA, and especially if it is supplied as a string, the `fix_region` will signal an error.

```{r, error = TRUE}
library(naijR)

fix_region("Legos Island")
```

The thinking is that an automated solution may not be necessary for a single value that was probably provided interactively.

We will now add another LGA so that the argument passed to the function is character vector with more that one element:

```{r}
fix_region(c("Legos Island", "Amuwo-Odofin"))
```

Sometimes when we use a character vector to perform this check, the function `fix_region` may encounter difficulty deciding what fixes to apply. In such instances, the best thing is to convert the vector into an `lgas` object. 

```{r, error = TRUE}
fix_region(c("Legos Island", "Amuwo Odofin"))
fix_region(lgas(c("Legos Island", "Amuwo Odofin")))
```

Note that the constructor `lgas()` should, by default, signal a warning when the vector we are supplying has misspelt LGAs; however, this warning is suppressed if `lgas()` is nested in `fix_region()`.

When the spelling mistakes depart far from the available LGA spellings, the user is shown a message stating that the fixes that could not be applied. To carry out a fix, we proceed to the next stage.

```{r}
fix_region(lgas(c("Orange County", "Amuwo Odofin")))
```

#### Interactive fixes
When the automatic fix is not feasible, the user has the option of doing it interactively by calling `fix_region` and setting its `interactive` argument to `TRUE`. By following the prompts, the misspelt LGA as well as possible replacements are presented. All the user needs to do is to select the desired replacement value. This is particularly useful when the user is not sure of what the correct spelling might be.

When a misspelt LGA has more than one match, the interactive approach is the viable option for effecting fixes.

```{r}
adamawa <- c("Fufure", "Demsa", "Machika", "Fufure", "Ganye", "Hong")

# check for misspelt LGAs and, if necessary, attempt to fix
if (!all(is_lga(adamawa)))
  adamawa <- fix_region(adamawa)
```

We see that the purported LGA 'Machika' matches more than one LGA in the country. The original intent was to use "Michika". To address it, we run `fix_region` interactively. This method is for class `lgas` so

```{r, eval=FALSE}
adamawa <- fix_region(lgas(adamawa), interactive = TRUE)
```


Next, the user is provided with a prompt to provide a search item for likely LGAs that would be an appropriate replacement for the misspelt one:


We now enter in the search term:

Upon clicking "OK", a list of possible matches comes up; in this instance, only one option is provided. The option 'RETRY' allows the user to reset the search term, 'SKIP' is to try out another misspelt item (where there are more than one) and 'QUIT' is to exit the interactive session.

When we broaden the search possibilities, more items are listed among the LGA candidates for the edit. In our example, we will provide *Mi* instead of *Mich*, so that more LGAs are matched:


```{r manual-fix, include=FALSE}
adamawa <- fix_region_manual(adamawa, "Machika", "Michika")
```

At the end of it all, the spellings are fixed.

```{r, results = 'markup'}
all(is_lga(adamawa))
```

#### Manual fixes
When spelling errors are identified and the correct one is known, then a manual fix can be applied. For this, we use the function `fix_region_manual` and its use is pretty straightforward:


```{r manual-fix, eval = FALSE}
```
