---
title: "nigeria-maps"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{nigeria-maps}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(naijR)
```
The need for relatively easy-to-use tools for mapping data on Nigeria was one of the motivations behind the development of this package. Not so much of low-level programming was done; rather a collection of pre-existing packages and idioms from the R ecosystem were employed and brought together to enable the user focus more on the actual visualization of data on the country map instead of the programming.

The key function for drawing Nigeria maps is called `map_ng()`. This uses data from the CIA World Database provided by the `mapdata` package to draw a simple outline map of Nigeria. This functionality was used in the initial release of this package and has been maintained as the default map.

```{r original-map}
map_ng()
```


At the time of writing this, there are 3 broad categories of maps had been enabled. They are:

1. Plain maps of the entire country and or states.
2. Plain maps with sub-national boundaries shown.
3. Coloured maps, notably choropleths

The flavour of geo-spatial data used in the package is of the vector type--and of these, it uses *point* and *polygon* data (the use *line* data is planned for future releases).

## Plain maps
```{r}

```

## Plain maps with boundaries
## Choropleth maps